Fluent statistical computing interfaces for biological data analysis

### 2020-07-08 Rmd/06-conclusion.Rmd
first pass at intro to conculsion

>>>>

In this thesis, I have designed tools to explore workflow steps
that are integral to modern biological data science. In particular, I have
implemented software that facilitates the wrangling, integration, and 
visualisation of high-throughput biological data in a principled and pragmatic
manner. Chapter \@ref(ch:plyranges), "plyranges: a grammar of genomic data
transformation" developed a new domain specific language for genomics data.
Chapter \@ref(ch:fluentGenomics), "Fluent genomics with plyranges and tximeta"
described techniques integrating data along the genome, and emphasised
the importance of interoperability between tools. Chapter \@ref(ch:intron),
"Exploratory coverage analysis with superintronic and plyranges", tackled data 
integration from a different angle by looking at multiple summaries
of variables measured along the genome to find regions of biological interest. 
Chapter \@ref(ch:tsne), "Casting multiple shadows: high-dimensional 
interactive data visualisation with tours and embeddings", explored pragmatic
approaches to high dimensional data visualisation in light of the rise of 
popular non-linear embedding methods.

The chapters
